---
title: "Kermit Perceptions Rank-based Test"
author: "Robert Heim"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Robert's first message in the document. 

If you are the collaborator:
-load the tidyverse
-read in the kermit data as 'kermit'
-make some side by side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

```

```{r}
kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist

```

Perform rank-based comparisons using Mann-Whitney U and Wilcoxon-signed rank

Question: Is there a significant difference in pre-talk ranks of Kermit for male and female respondents? 

```{r}

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)

# H0: There is not a signficant difference in ranks for male and female respondents.
# HA: There is a significant difference in ranks. 

mwu_kermit



```

There was no significant difference in ranks for male and female correspondents (W= 155.5, p= 0.4, alpha= 0.05).